---
title: "Using EwEvis"
author: "Marc Taylor"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---




```{r setup}
library(EwEvis)
library(rgl)
```

```{r, echo=FALSE}
library(knitr)
knit_hooks$set(webgl = hook_webgl)
```


## Required data 
```{r}
# Northern Humboldt Current Ecosystem (La Niña, Tam et al. 2008)
TEgm <- 0.1014 # mean transfer efficiency (trophic levels 2-4)
Ts <- c(27165, 22349, 1658, 266.3, 17.45, 0.607, 0.00515, 6e-06) # Throughout
Bs <- c(62.84, 147.1, 70.05, 20.61, 1.658, 0.084, 0.000657, 1e-06, 0) # Biomass
```



## 3d trophic boxes (Vbox3d)

### Comparison plot (biomass example)

```{r testgl, webgl=TRUE, fig.width = 6, fig.height = 5}
open3d()
# color palatte
pal <- colorRampPalette(c("green", "yellow", "red"), bias=3)
# Biomass
tmp1 <- Vbox3d(V=Bs[1:5], TL.len = 10, col=pal(5), add.scale = FALSE)
# Throughput
tmp2 <- Vbox3d(V=Ts[1:5], TL.len = 10, col=pal(5), add.scale = TRUE,  shift=c(dist(tmp1[[1]]$vb[1,1:2])*20,0,0), scale.len = 1000^(1/3)
)
```


## 3d trophic pyramid (Vpyramid3d)

### Effect of TEgm on top angle (throughput example)
```{r testgl2, webgl=TRUE, fig.width = 6, fig.height = 5}
open3d()
tmp <- Vpyramid3d(V=Ts[2:8], TEgm = 0.07, col=2:7, 
    add.scale = FALSE
)
tmp2 <- Vpyramid3d(V=Ts[2:8], TEgm = 0.1, col=2:7,
   shift=c(dist(tmp[[1]]$vb[1,1:2])*1.1,0,0),
   add.scale = FALSE
)
tmp3 <- Vpyramid3d(V=Ts[2:8], TEgm = 0.15, col=2:7,
  shift=c(dist(tmp[[1]]$vb[1,1:2])*1.1*2,0,0),
  add.scale = TRUE, scale.len = 1000^(1/3)
)

# add labels
pos <- data.frame(rbind(
  rowMeans(tmp[[7]]$vb),
  rowMeans(tmp2[[7]]$vb),
  rowMeans(tmp3[[7]]$vb)
))
names(pos) <- c("x", "y", "z", "w")

text3d(pos$x, y=pos$y, z = pos$z+3,
          text=paste("TE =", c("7%", "10%", "15%")),
       color="black", font=2
) 
```


## References
Tam, J., Taylor, M.H., Blaskovic, V., Espinoza, P., Michael Ballón, R., Díaz, E., Wosnitza-Mendo, C., Argüelles, J., Purca, S., Ayón, P., Quipuzcoa, L., Gutiérrez, D., Goya, E., Ochoa, N., Wolff, M., 2008. Trophic modeling of the Northern Humboldt Current Ecosystem, Part I: Comparing trophic linkages under La Niña and El Niño conditions. Progress in Oceanography 79, 352–365. doi:10.1016/j.pocean.2008.10.007
